Supplemental Materials, Methods and Results

### 2022-04-16 supp/Supplemental Materials and Methods.Rmd
changed data to data_wide through code. Makes it more clear

          data <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
      data$lat <- as.numeric(data$lat)
    new_papers <- data[-grep("_o", data$record_num),]
    old_papers <- data[grep("_o", data$record_num),]

    # Add full species to data
      data <- data %>%
              mutate(species_full = paste0(genus, " ",species))

    # habitat
      spp_habitat <- data %>%
                      group_by(habitat) %>%
                      summarise(spp_n = length(unique(species_full)))

      # Note that some species need to be replaced
      data <- data %>%
              mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
                                           "Mauremys reevesii", species_full)) %>%
              mutate(species_full = ifelse(species_full == "Enithares sp", 
                                           "Enithares ciliata", species_full))  %>%
              mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
              mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))

    # Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
      data <- data %>%
              mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
                     r1.2_sd = se_to_sd(r1.2_se, r1.2_N),
                     r2.1_sd = se_to_sd(r2.1_se, r2.1_N),
                     r2.2_sd = se_to_sd(r2.2_se, r2.2_N)) %>%
              dplyr::select(-c(r1.1_se, r1.2_se, r2.1_se, r2.2_se,
                               r1.1_CV, r1.2_CV, r2.1_CV, r2.2_CV, 
                               r1.1_logCV, r1.2_logCV, r2.1_logCV, r2.2_logCV))
##################################
## Calculate effect sizes
##################################
    # Calculate Q10 effect sizes and sampling variances; filter out non-finate values and clean up dataframe a bit

      data <- data %>%
             mutate(lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    obs = 1:n()) %>%
            dplyr::select(-c(data_source, source_page,phylum, class, order, family, genus, species, geo_location, details, notes)) %>%
                  filter_if(~is.numeric(.), all_vars(!is.infinite(.)))

@@

      data <- data %>%
              filter(!record_num == "p088_o")

      write.csv(data, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################

>>>>

          data_wide <- read.csv("../data/CombinedData_wide.csv", stringsAsFactors = FALSE)
      data_wide$lat <- as.numeric(data_wide$lat)
    new_papers <- data_wide[-grep("_o", data_wide$record_num),]
    old_papers <- data_wide[grep("_o", data_wide$record_num),]

    # Add full species to data
      data_wide <- data_wide %>%
              mutate(species_full = paste0(genus, " ",species))

    # habitat
      spp_habitat <- data_wide %>%
                      group_by(habitat) %>%
                      summarise(spp_n = length(unique(species_full)))

      # Note that some species need to be replaced
      data_wide <- data_wide %>%
              mutate(species_full = ifelse(species_full == "Chinemys reevesii", 
                                           "Mauremys reevesii", species_full)) %>%
              mutate(species_full = ifelse(species_full == "Enithares sp", 
                                           "Enithares ciliata", species_full))  %>%
              mutate(habitat = ifelse(species_full == "Pungitius pungitius", "m", habitat))  %>% # Fix a few errors in habitat classificaton
              mutate(habitat = ifelse(species_full == "Danio rerio", "f", habitat))

    # Convert se to SD so it can be used for effect sizes. Drop out the SE columns as these are no longer needed
      data_wide <- data_wide %>%
              mutate(r1.1_sd = se_to_sd(r1.1_se, r1.1_N),
                     r1.2_sd = se_to_sd(r1.2_se, r1.2_N),
                     r2.1_sd = se_to_sd(r2.1_se, r2.1_N),
                     r2.2_sd = se_to_sd(r2.2_se, r2.2_N)) %>%
              dplyr::select(-c(r1.1_se, r1.2_se, r2.1_se, r2.2_se,
                               r1.1_CV, r1.2_CV, r2.1_CV, r2.2_CV, 
                               r1.1_logCV, r1.2_logCV, r2.1_logCV, r2.2_logCV))
##################################
## Calculate effect sizes
##################################
    # Calculate Q10 effect sizes and sampling variances; filter out non-finate values and clean up dataframe a bit

      data_wide <- data_wide %>%
             mutate(lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnRR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r1.2, sd1=r1.1_sd, sd2=r1.2_sd, n1=r1.1_N, n2=r1.2_N, 
                             name = "acute_t1"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r2.1, r2=r2.2, sd1=r2.1_sd, sd2=r2.2_sd, n1=r2.1_N, n2=r2.2_N, 
                             name = "acute_t2"),
                    lnCVR_Q10(t2=temp_2, t1=temp_1, r1=r1.1, r2=r2.2, sd1=r1.1_sd, sd2=r2.2_sd, n1=r1.1_N, n2=r2.2_N, 
                             name = "acclim"),
                    obs = 1:n()) %>%
            dplyr::select(-c(data_source, source_page,phylum, class, order, family, genus, species, geo_location, details, notes)) %>%
                  filter_if(~is.numeric(.), all_vars(!is.infinite(.)))

@@

      data_wide <- data_wide %>%
              filter(!record_num == "p088_o")

      write.csv(data_wide, file = "../output/data/data_final_wide.csv", row.names = FALSE)
##################################
## Re-organise the data frame
##################################
        ################ THIS SHOULD FIX THE DATA_LONG problems
      data_long_t <- data_wide %>%
                    pivot_longer(cols = c(27, 29, 31, 33, 35, 37, 39, 41, 43)) %>% 
                    mutate(type = ifelse(grepl("acute", name), "acute", "acclim")) %>% data.frame()
